A pipeline to analyse time-course gene expression data

### 2020-08-31 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2020-08-19 18:14:47.

@@

\texttt{moanin} is available from GitHub, and can be installed using the \texttt{install\_github} function in the package \texttt{devtools}, along with the corresponding package that contains time course datasets we will use:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(devtools)}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"NelleV/moanin"}\NormalTok{)}
\KeywordTok{install_github}\NormalTok{(}\StringTok{"NelleV/timecoursedata"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{BiocManager}\OperatorTok{::}\KeywordTok{install}\NormalTok{(}
    \KeywordTok{c}\NormalTok{(}\StringTok{"NMF"}\NormalTok{, }\StringTok{"ggfortify"}\NormalTok{, }\StringTok{"topGO"}\NormalTok{, }\StringTok{"biomaRt"}\NormalTok{,}
      \StringTok{"KEGGprofile"}\NormalTok{, }\StringTok{"BiocWorkflowTools"}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

This workflow is illustrated using data from a micro-array time-course
experiment, exposing mice to three different strains of influenza, and
collecting lung tissue during 14 time-points after infection (0, 3, 6, 9, 12,
18, 24, 30, 36, 48, 60 hours, then 3, 5, and 7 days later)
\citep{shoemaker:ultrasensitive}. The three strains of influenza used in the
study are (1) a low pathogenicity seasonal H1N1 influenza virus
(A/Kawasaki/UTK4/2009 {[}H1N1{]}), a mildly pathogenic virus from the 2009
pandemic season (A/California/04/2009 {[}H1N1{]}), and a highly pathogenic H5N1
avian influenza virus (A/Vietnam/1203/2004 {[}H5N1{]}. Mice were injected with
\(10^5\) PFU of each virus. An adidtional 42 mice were injected with a lower dose
of the Vietnam avian influenza virus (\(10^3\) PFU).

@@

##  [3] ggfortify_0.4.10            timecoursedata_0.99.15     

>>>>

@@

\texttt{moanin} and \texttt{timecoursedata} are available from bioconductor, and can be
installed using the \texttt{install} function in the package \texttt{BiocManager}, along
with the corresponding package that contains time course datasets we will use:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(BiocManager)}
\CommentTok{# Need to use the development version for now.}
\NormalTok{BiocManager}\OperatorTok{::}\KeywordTok{install}\NormalTok{(}\DataTypeTok{version=}\StringTok{"devel"}\NormalTok{)}
\NormalTok{BiocManager}\OperatorTok{::}\KeywordTok{valid}\NormalTok{()}

\NormalTok{BiocManager}\OperatorTok{::}\KeywordTok{install}\NormalTok{(}\StringTok{"timecoursedata"}\NormalTok{)}
\NormalTok{BiocManager}\OperatorTok{::}\KeywordTok{install}\NormalTok{(}\StringTok{"moanin"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{BiocManager}\OperatorTok{::}\KeywordTok{install}\NormalTok{(}
    \KeywordTok{c}\NormalTok{(}\StringTok{"NMF"}\NormalTok{, }\StringTok{"ggfortify"}\NormalTok{, }\StringTok{"topGO"}\NormalTok{, }\StringTok{"biomaRt"}\NormalTok{,}
      \StringTok{"KEGGprofile"}\NormalTok{, }\StringTok{"BiocWorkflowTools"}\NormalTok{, }\StringTok{"timecoursedata"}\NormalTok{, ))}
\end{Highlighting}
\end{Shaded}

@@

This workflow is illustrated using data from a micro-array time-course
experiment, exposing mice to three different strains of influenza, and
collecting lung tissue during 14 time-points after infection (0, 3, 6, 9, 12,
18, 24, 30, 36, 48, 60 hours, then 3, 5, and 7 days later)
\citep{shoemaker:ultrasensitive}. The three strains of influenza used in the
study are (1) a low pathogenicity seasonal H1N1 influenza virus
(A/Kawasaki/UTK4/2009 {[}H1N1{]}), a mildly pathogenic virus from the 2009
pandemic season (A/California/04/2009 {[}H1N1{]}), and a highly pathogenic H5N1
avian influenza virus (A/Vietnam/1203/2004 {[}H5N1{]}. Mice were injected with
\(10^5\) PFU of each virus. An additional 42 mice were injected with a lower dose
of the Vietnam avian influenza virus (\(10^3\) PFU).

@@

##  [3] ggfortify_0.4.10            timecoursedata_0.99.17     
